\documentclass[]{rahulworld-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Shreshthajit Das}\\
\end{large}
3rd Year (Bsc)\\
Software   Engineering\\ 
at Shahjalal University of Science and Technology,Sylhet.
 \\ 
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}

Github:// \href{https://github.com/shreshthajit}{\custombold{shreshthajit}} \\
Toph://  \href{https://toph.co/u/SDJ_sust}{\custombold{SDJ_sust}} \\
Stopstalk://  \href{https://www.stopstalk.com/user/profile/shreshthajit5}{\custombold{shreshthajit5}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
Ubuntu Linux, Windows
\vspace{6pt}
\subsection{Languages}
C/C++, Java, Python,javascript
\vspace{6pt}
\vspace{6pt}
\subsection{Databases}
MySQL
\vspace{6pt}
\subsection{Others}
Git,\\Sublime Text, Eclipse,\\
visual Studio,Latex\\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures\\
Algorithm\\
Discrete Mathematics\\
Operating Systems\\
MySQL\\
Computer Data and Network Security\\
Introduction to Data Science\\
Typing speed:65wpm at Typeracer\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2017-2022}
\subsection{Bsc in Software Engineering}
Shahjalal University of Science and Technology,Sylhet \\

\vspace{8pt}
\datecolor{2015-2017}
\subsection{Intermediate}
M.C College,Sylhet\\
GPA:5.00

\vspace{8pt}
\datecolor{2007-2015}
\subsection{High School}
Govt. Jubilee High School,Sunamganj\\
GPA:5.00
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill IICT, SUST, Sylhet \\
\hspace*{0pt}\hfill Sylhet, Alpona-47, Bangladesh \\
\hspace*{0pt}\hfill Mob.: +880-1645623079 \\
\hspace*{0pt}\hfill Email.:\textbf{\href{mailto:jisnu1024@gmail.com}{jisnu@gmail.com}} \\
%\hspace*{0pt}\hfill Web.:\textbf{\href{http://rahulchauhan.net}{http://rahulchauhan.net}} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Project}
\noindent\rule{12.5cm}{0.4pt}



\datecolor{2018:} \runsubsection{Game Project: Run For Life}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Environment:SFML,codeblocks\\
 The name of our game is run for life. There will be some enemy and a shooter will try to chase them. The shooter can gain coin by running through.
\end{minipage}






 


\datecolor{2019:} \runsubsection{Java Game Porject: Chess}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
This is basically to learn java by making this game
\end{minipage}






\datecolor{2020:} \runsubsection{E-Commerce site:}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Environment: Php,Javascript,bootstrap,Mysql.\\
The objective of this project is to develop a general purpose e-commerce store where electronic accessories   can be bought from the comfort of home through the internet. 
\end{minipage}





\datecolor{2021} \runsubsection{File Share(Networking Project)}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Client to Server File Transfer Application
Using TCP in Java.
\end{minipage}







\section{Competitive Programming Achievements} 

\noindent\rule{12.5cm}{0.4pt}
\datecolor{Contests:} \runsubsection{Participated 80+ Online and Offline Contests}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Participated in various platform like Codeforces,Atcoder,Toph,Chodechef and Vjudge contests.
\end{minipage}




\datecolor{Problem Solved:} \runsubsection{Solved Problem in various online judges}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Solved 900 problems on various online Judges.On codeforces solved 690 problem and the rest are solved in other judges like Uva,Atcoder,Spoj etc
\end{minipage}



 
 


\datecolor{Interest:} \runsubsection{Alghorithmic Problem}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Solved various problem using Dp,Hashing,Number-theory,Graph-theory,String etc.
\end{minipage}


\end{minipage} 
\end{document}  \documentclass[]{article}
